The ANthropological Notation Ontology (ANNO): A core ontology for annotating human bones and deriving phenotypes

### 2024-02-15 paper.tex
MLH changes 2024-02-15 _3
MLH changes 2024-02-15 _4

\subsubsection{Existing ontologies: FMA}\label{sec:OntologiesFMA}

@@

Further contributions of ANNO include ensuring consistent Latin declension, including the plural form; enhancing transparency with detailed source references, distinguishing between original (primary) and citing (core) sources in the case of measurements. The ontology dissects group structures into atomic bone parts and more moreover introduces new terms and definitions for landmarks such as joint surfaces, which, despite their anthropological relevance, often remain unnamed in anatomy literature. It also formally establishes terms for osteometric measurement points outside the skull, addressing gaps not covered in existing literature.

>>>>

\subsubsection{Existing ontologies: Foundational Model of Anatomy (FMA)}\label{sec:OntologiesFMA}

@@

Further contributions of ANNO include ensuring consistent Latin declension, including the plural form; enhancing transparency with detailed source references, distinguishing between original (primary) and citing (core) sources in the case of measurements. The ontology dissects group structures into atomic bone parts and more moreover introduces new terms and definitions for landmarks such as joint surfaces, which, despite their anthropological relevance, often remain unnamed in anatomy literature. It also formally establishes terms for osteometric measurement points outside the skull, addressing gaps not covered in the existing literature.
